\documentclass[10pt]{article}
%% Specify the Express journal you are submitting to
%\usepackage[OME]{express}
\usepackage[OE]{express}
%\usepackage[BOE]{express}

\begin{document}
\title{Motivational Letter for Extremism \& Democracy Summer School}

\author{Fabio Votta,\authormark{1} Q. Nga Nguyen,\authormark{2} and Marlon Schumacher\authormark{3}}

\address{\authormark{1}B.A. University of Stuttgart, Department for Empirical Social Research, \href{fabio.votta@gmail.com}{fabio.votta@gmail.com}\\
\authormark{2}B.A. Institut d'Etudes Politiques de Bordeaux/ University of Stuttgart,\\ Department of Political Theory and Empirical Democracy Research,  \href{nga.nguyen@scpobx.fr}{nga.nguyen@scpobx.fr}\\
\authormark{3}B.A. University of Stuttgart, Frauenhofer Society, 
\href{M.C.Schumacher@live.de}{m.c.schumacher@live.de}}

%\email{\authormark{*}opex@osa.org} %% email address is required

% \homepage{http:...} %% author's URL, if desired

%%%%%%%%%%%%%%%%%%% abstract and OCIS codes %%%%%%%%%%%%%%%%
%% [use \begin{abstract*}...\end{abstract*} if exempt from copyright]

%%%%%%%%%%%%%%%%%%%%%%%%%%  body  %%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.4cm}
\begin{center}
\noindent \textbf{\large 1st Summer School of the ECPR standing group on Extremism and Democracy \\on \textsc{concepts and methods for research on far-right politics}}
\end{center}
\vspace{0.2cm}

\noindent Dear Sirs or Madams,

\vspace{0.3cm}

having recently addressed the question of how to best empirically approach \textit{traditionalist populism} - a variant of populism that exhibits Cas Mudde's proposed features of the far right, we wish to participate at your summer school to critically discuss our findings. To our knowledge, scholarship studying the phenomenon of populism is still plagued with conceptual conflations between populism and the far right, leading to shortcomings in empirical analyses. We seek to disentangle these concepts, with the aim of better understanding:
\begin{enumerate}
\item those elements that explain populism, 
\item those that explain far right attitudes, and ultimately
\item those that lead to interactions between these two phenomena.
\end{enumerate}

We are three aspiring young researchers, currently completing the M.A. \textit{Empirical Political and Social Research} at the University of Stuttgart (Germany) and at the Institut d'Etudes Politiques de Bordeaux (France). Having worked on a wide range of topics and being equipped with versatile methods, we hope to contribute to your school's goal of "bolster[ing] and promot[ing] knowledge on the theoretical, empirical, and methodological underpinnings of contemporary far-right politics". The research expertise that we will hopefully be able to bring to the seminar includes:

\vspace{0.15cm}

\textbf{Conceptually speaking:}
\begin{itemize}
\item Political extremism (esp. focus on interactions between religion and politics) - \textit{F. Votta}
\item International conflict studies (esp. focus on manifestations of left and right-wing terrorism since the 19th century in civil and international conflicts) - \textit{N. Nguyen}
\item Political outcomes of societal upheavals (esp. focus on the Middle East) - \textit{M. Schumacher}
\end{itemize}

\textbf{Methodologically speaking:}
\begin{itemize}
\item Advanced computational methods (esp. automatic web scraping \& machine learning) - \textit{F. Votta}
\item Mixed methods (esp. qualitative-quantitative content analysis) - \textit{N. Nguyen}
\item Advanced quantitative methods (esp. multilevel modeling) - \textit{M. Schumacher}
\end{itemize}

As the summer school will assemble highly influential scholars in the field, we hope to enter into a fruitful dialogue in which both established and aspiring researchers can share their ideas. Especially the presence of Cas Mudde, whose work greatly influenced our analyses, will give us the opportunity to receive feedback about the conceptual framework that we propose. This is important for us, as it helps us refine our conceptualization of populism, which hopefully sets off more nuanced discussions about the nature of this phenomenon.

On a last note, we would like to express our wish to compete for the grants offered by the ECPR, as we belong to the University of Stuttgart, an ECPR member institution. However, we understand that funding opportunities are limited. If it is not possible to compete for several grants as a team, we are willing to share the remaining costs, as long as we can seize the opportunity to be part of this thrilling learning experience. 

\end{document}
