---
title: "Populism Data Wrangling"
output: html_notebook
---

# Loading in Data and packages

```{r}
load("data/ess_vote.Rdata")

pacman::p_load(tidyverse, writexl, haven, sjPlot, sjmisc, texreg, car, psych, knitr, labelled, broom, magrittr, BaylorEdPsych, lmtest, datapasta, brms, questionr)

# ess %<>%
#   select(-prtmb, -prtcl, -prtvt)
```


# Populistische Parteien umkodieren

## Partyvote

```{r}

parties <- ess[, stringr::str_detect(names(ess), "prtv")] %>% 
  mutate_all(sjmisc::to_label) %>% 
  mutate_all(as.character)

table(ess$prtvt)

ess <- parties %>% 
  mutate(prtvt = case_when(
    !is.na(prtvtat) ~ prtvtat,
    !is.na(prtvtaat) ~ prtvtaat,
    !is.na(prtvtbat) ~ prtvtbat,
    !is.na(prtvtbe)  ~ prtvtbe,
    !is.na(prtvtabe) ~ prtvtabe,
    !is.na(prtvtbbe) ~ prtvtbbe,
    !is.na(prtvtcbe) ~ prtvtcbe,
    !is.na(prtvtbg)  ~ prtvtbg,
    !is.na(prtvtabg) ~ prtvtabg,
    !is.na(prtvtbbg) ~ prtvtbbg,
    !is.na(prtvtcbg) ~ prtvtcbg,
    !is.na(prtvtch)  ~ prtvtch,
    !is.na(prtvtach) ~ prtvtach,
    !is.na(prtvtbch) ~ prtvtbch,
    !is.na(prtvtcch) ~ prtvtcch,
    !is.na(prtvtdch) ~ prtvtdch,
    !is.na(prtvtech) ~ prtvtech,
    !is.na(prtvtcy)  ~ prtvtcy,
    !is.na(prtvtacy) ~ prtvtacy,
    !is.na(prtvtcz)  ~ prtvtcz,
    !is.na(prtvtacz) ~ prtvtacz,
    !is.na(prtvtbcz) ~ prtvtbcz,
    !is.na(prtvtccz) ~ prtvtccz,
    !is.na(prtvtdcz) ~ prtvtdcz,
    # !is.na(prtvde1)  ~ prtvde1,
    # !is.na(prtvade1) ~ prtvade1,
    # !is.na(prtvbde1) ~ prtvbde1,
    # !is.na(prtvcde1) ~ prtvcde1,
    # !is.na(prtvdde1) ~ prtvdde1,
    # !is.na(prtvede1) ~ prtvede1,
    !is.na(prtvde2)  ~ prtvde2,
    !is.na(prtvade2) ~ prtvade2,
    !is.na(prtvbde2) ~ prtvbde2,
    !is.na(prtvcde2) ~ prtvcde2,
    !is.na(prtvdde2) ~ prtvdde2,
    !is.na(prtvede2) ~ prtvede2,
    !is.na(prtvtdk)  ~ prtvtdk,
    !is.na(prtvtadk) ~ prtvtadk,
    !is.na(prtvtbdk) ~ prtvtbdk,
    !is.na(prtvtcdk) ~ prtvtcdk,
    !is.na(prtvtee)  ~ prtvtee,
    !is.na(prtvtaee) ~ prtvtaee,
    !is.na(prtvtbee) ~ prtvtbee,
    !is.na(prtvtcee) ~ prtvtcee,
    !is.na(prtvtdee) ~ prtvtdee,
    !is.na(prtvteee) ~ prtvteee,
    !is.na(prtvtes)  ~ prtvtes,
    !is.na(prtvtaes) ~ prtvtaes,
    !is.na(prtvtbes) ~ prtvtbes,
    !is.na(prtvtces) ~ prtvtces,
    !is.na(prtvtfi)  ~ prtvtfi,
    !is.na(prtvtafi) ~ prtvtafi,
    !is.na(prtvtbfi) ~ prtvtbfi,
    !is.na(prtvtcfi) ~ prtvtcfi,
    !is.na(prtvtfr)  ~ prtvtfr,
    !is.na(prtvtafr) ~ prtvtafr,
    !is.na(prtvtbfr) ~ prtvtbfr,
    !is.na(prtvtcfr) ~ prtvtcfr,
    !is.na(prtvtgb)  ~ prtvtgb,
    !is.na(prtvtagb) ~ prtvtagb,
    !is.na(prtvtbgb) ~ prtvtbgb,
    !is.na(prtvtgr)  ~ prtvtgr,
    !is.na(prtvtagr) ~ prtvtagr,
    !is.na(prtvtbgr) ~ prtvtbgr,
    !is.na(prtvtcgr) ~ prtvtcgr,
    !is.na(prtvthr)  ~ prtvthr,
    !is.na(prtvthu)  ~ prtvthu,
    !is.na(prtvtahu) ~ prtvtahu,
    !is.na(prtvtbhu) ~ prtvtbhu,
    !is.na(prtvtchu) ~ prtvtchu,
    !is.na(prtvtdhu) ~ prtvtdhu,
    !is.na(prtvtehu) ~ prtvtehu,
    !is.na(prtvtie)  ~ prtvtie,
    !is.na(prtvtaie) ~ prtvtaie,
    !is.na(prtvtil)  ~ prtvtil,
    !is.na(prtvtail) ~ prtvtail,
    !is.na(prtvtbil) ~ prtvtbil,
    !is.na(prtvtcil) ~ prtvtcil,
    !is.na(prtvtis)  ~ prtvtis,
    !is.na(prtvtais) ~ prtvtais,
    !is.na(prtvtit)  ~ prtvtit,
    !is.na(prtvtait) ~ prtvtait,
    !is.na(prtvtbit) ~ prtvtbit,
    !is.na(prtvlt1)  ~ prtvlt1,
    !is.na(prtvalt1) ~ prtvalt1,
    # !is.na(prtvlt2)  ~ prtvlt2,
    # !is.na(prtvalt2) ~ prtvalt2,
    # !is.na(prtvlt3)  ~ prtvlt3,
    # !is.na(prtvalt3) ~ prtvalt3,
    !is.na(prtvtlu)  ~ prtvtlu,
    !is.na(prtvtnl)  ~ prtvtnl,
    !is.na(prtvtanl) ~ prtvtanl,
    !is.na(prtvtbnl) ~ prtvtbnl,
    !is.na(prtvtcnl) ~ prtvtcnl,
    !is.na(prtvtdnl) ~ prtvtdnl,
    !is.na(prtvtenl) ~ prtvtenl,
    !is.na(prtvtfnl) ~ prtvtfnl,
    !is.na(prtvtno)  ~ prtvtno,
    !is.na(prtvtano) ~ prtvtano,
    !is.na(prtvtbno) ~ prtvtbno,
    !is.na(prtvtpl)  ~ prtvtpl,
    !is.na(prtvtapl) ~ prtvtapl,
    !is.na(prtvtbpl) ~ prtvtbpl,
    !is.na(prtvtcpl) ~ prtvtcpl,
    !is.na(prtvtpt)  ~ prtvtpt,
    !is.na(prtvtapt) ~ prtvtapt,
    !is.na(prtvtbpt) ~ prtvtbpt,
    !is.na(prtvtru)  ~ prtvtru,
    !is.na(prtvtaru) ~ prtvtaru,
    !is.na(prtvtbru) ~ prtvtbru,
    !is.na(prtvtcru) ~ prtvtcru,
    !is.na(prtvtse)  ~ prtvtse,
    !is.na(prtvtase) ~ prtvtase,
    !is.na(prtvtbse) ~ prtvtbse,
    !is.na(prtvtsi)  ~ prtvtsi,
    !is.na(prtvtasi) ~ prtvtasi,
    !is.na(prtvtbsi) ~ prtvtbsi,
    !is.na(prtvtcsi) ~ prtvtcsi,
    !is.na(prtvtdsi) ~ prtvtdsi,
    !is.na(prtvtesi) ~ prtvtesi,
    !is.na(prtvtsk)  ~ prtvtsk,
    !is.na(prtvtask) ~ prtvtask,
    !is.na(prtvtbsk) ~ prtvtbsk,
    !is.na(prtvtcsk) ~ prtvtcsk,
    !is.na(prtvttr)  ~ prtvttr,
    !is.na(prtvtatr) ~ prtvtatr,
    !is.na(prtvtua)  ~ prtvtua,
    !is.na(prtvtaua) ~ prtvtaua,
    !is.na(prtvtbua) ~ prtvtbua,
    !is.na(prtvtcua) ~ prtvtcua,
    !is.na(prtvtfch) ~ prtvtfch,
    !is.na(prtvtfee) ~ prtvtfee,
    !is.na(prtvtdfi) ~ prtvtdfi,
    !is.na(prtvtbie) ~ prtvtbie,
    !is.na(prtvtbis) ~ prtvtbis,
    !is.na(prtvtdpl) ~ prtvtdpl,
    !is.na(prtvtdru) ~ prtvtdru)) %>% 
  select(prtvt) %>% 
  cbind(ess)



table(ess$prtvt)

#save(ess, file = "data/ess.Rdata")
```

## Partyclose

```{r}
parties2 <- ess[, stringr::str_detect(names(ess), "prtc")] %>% 
  mutate_all(sjmisc::to_label) %>% 
  mutate_all(as.character)

dput(names(parties2))

ess <- parties2 %>% 
  mutate(prtcl = case_when(
  !is.na(prtclat) ~  prtclat ,
  !is.na(prtclaat) ~ prtclaat,
  !is.na(prtclcat) ~ prtclcat  ,
  !is.na(prtclbe) ~  prtclbe  ,
  !is.na(prtclabe) ~ prtclabe  ,
  !is.na(prtclbbe) ~ prtclbbe  ,
  !is.na(prtclcbe) ~ prtclcbe  ,
  !is.na(prtclbg) ~  prtclbg ,
  !is.na(prtclabg) ~ prtclabg  ,
  !is.na(prtclbbg) ~ prtclbbg ,
  !is.na(prtclcbg) ~ prtclcbg  ,
  !is.na(prtclch) ~  prtclch ,
  !is.na(prtclach) ~ prtclach  ,
  !is.na(prtclbch) ~ prtclbch  ,
  !is.na(prtclcch) ~ prtclcch  ,
  !is.na(prtcldch) ~ prtcldch  ,
  !is.na(prtclech) ~ prtclech  ,
  !is.na(prtclcy) ~  prtclcy ,
  !is.na(prtclacy) ~ prtclacy  ,
  !is.na(prtclcz) ~  prtclcz ,
  !is.na(prtclacz) ~ prtclacz  ,
  !is.na(prtclbcz) ~ prtclbcz  ,
  !is.na(prtclccz) ~ prtclccz  ,
  !is.na(prtcldcz) ~ prtcldcz  ,
  !is.na(prtclde) ~  prtclde ,
  !is.na(prtclade) ~ prtclade  ,
  !is.na(prtclbde) ~ prtclbde  ,
  !is.na(prtclcde) ~ prtclcde  ,
  !is.na(prtcldde) ~ prtcldde  ,
  !is.na(prtclede) ~ prtclede  ,
  !is.na(prtcldk) ~  prtcldk ,
  !is.na(prtcladk) ~ prtcladk  ,
  !is.na(prtclbdk) ~ prtclbdk  ,
  !is.na(prtclcdk) ~ prtclcdk  ,
  !is.na(prtclee) ~  prtclee ,
  !is.na(prtclaee) ~ prtclaee  ,
  !is.na(prtclbee) ~ prtclbee  ,
  !is.na(prtclcee) ~ prtclcee  ,
  !is.na(prtcldee) ~ prtcldee  ,
  !is.na(prtcleee) ~ prtcleee  ,
  !is.na(prtcles) ~  prtcles ,
  !is.na(prtclaes) ~ prtclaes  ,
  !is.na(prtclbes) ~ prtclbes  ,
  !is.na(prtclces) ~ prtclces  ,
  !is.na(prtcldes) ~ prtcldes  ,
  !is.na(prtclfi) ~  prtclfi ,
  !is.na(prtclafi) ~ prtclafi  ,
  !is.na(prtclbfi) ~ prtclbfi  ,
  !is.na(prtclcfi) ~ prtclcfi  ,
  !is.na(prtclfr) ~  prtclfr,
  !is.na(prtclafr) ~ prtclafr  ,
  !is.na(prtclbfr) ~ prtclbfr  ,
  !is.na(prtclcfr) ~ prtclcfr  ,
  !is.na(prtcldfr) ~ prtcldfr  ,
  !is.na(prtclgb) ~  prtclgb,
  !is.na(prtclagb) ~ prtclagb ,
  !is.na(prtclbgb) ~ prtclbgb  ,
  !is.na(prtclgr) ~  prtclgr ,
  !is.na(prtclagr) ~ prtclagr  ,
  !is.na(prtclbgr) ~ prtclbgr  ,
  !is.na(prtclcgr) ~ prtclcgr  ,
  !is.na(prtclhr) ~  prtclhr  ,
  !is.na(prtclhu) ~  prtclhu ,
  !is.na(prtclahu) ~  prtclahu ,
  !is.na(prtclbhu) ~  prtclbhu ,
  !is.na(prtclchu) ~  prtclchu ,
  !is.na(prtcldhu) ~  prtcldhu ,
  !is.na(prtclehu) ~  prtclehu ,
  !is.na(prtclie) ~  prtclie ,
  !is.na(prtclaie) ~ prtclaie  ,
  !is.na(prtclbie) ~ prtclbie  ,
  !is.na(prtclil) ~  prtclil ,
  !is.na(prtclail) ~ prtclail  ,
  !is.na(prtclbil) ~ prtclbil  ,
  !is.na(prtclcil) ~ prtclcil  ,
  !is.na(prtcldil) ~ prtcldil  ,
  !is.na(prtclis) ~  prtclis ,
  !is.na(prtclais) ~ prtclais  ,
  !is.na(prtclit) ~  prtclit ,
  !is.na(prtclait) ~ prtclait  ,
  !is.na(prtclbit) ~ prtclbit  ,
  !is.na(prtcllu) ~ prtcllu  ,
  !is.na(prtcllt) ~ prtcllt  ,
  !is.na(prtclalt) ~ prtclalt  ,
  !is.na(prtclnl) ~ prtclnl  ,
  !is.na(prtclanl) ~ prtclanl  ,
  !is.na(prtclbnl) ~ prtclbnl,
  !is.na(prtclcnl) ~ prtclcnl  ,
  !is.na(prtcldnl) ~ prtcldnl  ,
  !is.na(prtclenl) ~ prtclenl  ,
  !is.na(prtclno) ~  prtclno ,
  !is.na(prtclano) ~ prtclano  ,
  !is.na(prtclbno) ~ prtclbno  ,
  !is.na(prtclpl) ~  prtclpl ,
  !is.na(prtclapl) ~  prtclapl ,
  !is.na(prtclbpl) ~  prtclbpl ,
  !is.na(prtclcpl) ~  prtclcpl ,
  !is.na(prtcldpl) ~  prtcldpl ,
  !is.na(prtclepl) ~  prtclepl ,
  !is.na(prtclfpl) ~  prtclfpl ,
  !is.na(prtclpt) ~  prtclpt ,
  !is.na(prtclapt) ~ prtclapt  ,
  !is.na(prtclbpt) ~ prtclbpt  ,
  !is.na(prtclcpt) ~ prtclcpt  ,
  !is.na(prtcldpt) ~ prtcldpt  ,
  !is.na(prtclru) ~  prtclru ,
  !is.na(prtclaru) ~ prtclaru  ,
  !is.na(prtclbru) ~ prtclbru  ,
  !is.na(prtclcru) ~ prtclcru  ,
  !is.na(prtclse) ~  prtclse ,
  !is.na(prtclase) ~ prtclase  ,
  !is.na(prtclbse) ~ prtclbse  ,
  !is.na(prtclsi) ~  prtclsi ,
  !is.na(prtclasi) ~ prtclasi  ,
  !is.na(prtclbsi) ~ prtclbsi  ,
  !is.na(prtclcsi) ~ prtclcsi  ,
  !is.na(prtcldsi) ~ prtcldsi  ,
  !is.na(prtclesi) ~ prtclesi  ,
  !is.na(prtclsk) ~  prtclsk ,
  !is.na(prtclask) ~ prtclask  ,
  !is.na(prtclbsk) ~ prtclbsk  ,
  !is.na(prtclcsk) ~ prtclcsk  ,
  !is.na(prtcltr) ~  prtcltr,
  !is.na(prtclatr) ~ prtclatr  ,
  !is.na(prtclua) ~  prtclua ,
  !is.na(prtclaua) ~ prtclaua  ,
  !is.na(prtclbua) ~ prtclbua  ,
  !is.na(prtclcua) ~ prtclcua  ,
  !is.na(prtcldua) ~ prtcldua  ,
  !is.na(prtclfch) ~ prtclfch  ,
  !is.na(prtclfee) ~ prtclfee  ,
  !is.na(prtcldfi) ~ prtcldfi  ,
  !is.na(prtclefr) ~ prtclefr  ,
  !is.na(prtclcie) ~ prtclcie  ,
  !is.na(prtclbis) ~ prtclbis  ,
  !is.na(prtclgpl) ~ prtclgpl  ,
  !is.na(prtcldru) ~ prtcldru
  ))  %>% 
  select(prtcl) %>% 
  cbind(ess)

table(ess$prtcl)

#populist_parties
```


## Partymember

```{r}
#load("data/ess.Rdata")

parties3 <- ess[, stringr::str_detect(names(ess), "prtmb")] %>% 
  mutate_all(sjmisc::to_label) %>% 
  mutate_all(as.character)

dput(names(parties3))

ess <- parties3 %>% 
  mutate(prtmb = case_when(
  !is.na(prtmbat) ~  prtmbat ,
  !is.na(prtmbaat) ~ prtmbaat,
  !is.na(prtmbbe) ~ prtmbbe  ,
  !is.na(prtmbabe) ~  prtmbabe  ,
  !is.na(prtmbbbe) ~ prtmbbbe  ,
  !is.na(prtmbcbe) ~ prtmbcbe  ,
  !is.na(prtmbbg) ~ prtmbbg  ,
  !is.na(prtmbabg) ~  prtmbabg ,
  !is.na(prtmbbbg) ~ prtmbbbg  ,
  !is.na(prtmbch) ~ prtmbch ,
  !is.na(prtmbach) ~ prtmbach  ,
  !is.na(prtmbbch) ~  prtmbbch ,
  !is.na(prtmbcch) ~ prtmbcch  ,
  !is.na(prtmbcy) ~ prtmbcy  ,
  !is.na(prtmbcz) ~ prtmbcz  ,
  !is.na(prtmbacz) ~ prtmbacz  ,
  !is.na(prtmbbcz) ~ prtmbbcz  ,
  !is.na(prtmbde) ~  prtmbde ,
  !is.na(prtmbade) ~ prtmbade  ,
  !is.na(prtmbbde) ~  prtmbbde ,
  !is.na(prtmbcde) ~ prtmbcde  ,
  !is.na(prtmbdk) ~ prtmbdk  ,
  !is.na(prtmbadk) ~ prtmbadk  ,
  !is.na(prtmbbdk) ~ prtmbbdk  ,
  !is.na(prtmbee) ~  prtmbee ,
  !is.na(prtmbaee) ~ prtmbaee  ,
  !is.na(prtmbbee) ~  prtmbbee ,
  !is.na(prtmbcee) ~  prtmbcee,
  !is.na(prtmbes) ~  prtmbes,
  !is.na(prtmbaes) ~  prtmbaes,
  !is.na(prtmbbes) ~  prtmbbes,
  !is.na(prtmbfi) ~  prtmbfi,
  !is.na(prtmbafi) ~  prtmbafi,
  !is.na(prtmbbfi) ~  prtmbbfi,
  !is.na(prtmbfr) ~  prtmbfr,
  !is.na(prtmbafr) ~  prtmbafr,
  !is.na(prtmbbfr) ~  prtmbbfr,
  !is.na(prtmbcfr) ~  prtmbcfr,
  !is.na(prtmbgb) ~  prtmbgb,
  !is.na(prtmbagb) ~  prtmbagb,
  !is.na(prtmbgr) ~  prtmbgr,
  !is.na(prtmbagr) ~  prtmbagr,
  !is.na(prtmbbgr) ~  prtmbbgr,
  !is.na(prtmbcgr) ~  prtmbcgr,
  !is.na(prtmbhr) ~  prtmbhr,
  !is.na(prtmbhu) ~  prtmbhu,
  !is.na(prtmbahu) ~  prtmbahu,
  !is.na(prtmbbhu) ~  prtmbbhu,
  !is.na(prtmbchu) ~  prtmbchu,
  !is.na(prtmbie) ~  prtmbie,
  !is.na(prtmbaie) ~  prtmbaie,
  !is.na(prtmbil) ~  prtmbil,
  !is.na(prtmbail) ~  prtmbail,
  !is.na(prtmbbil) ~  prtmbbil,
  !is.na(prtmbit) ~  prtmbit,
  !is.na(prtmbait) ~  prtmbait,
  !is.na(prtmblu) ~  prtmblu,
  !is.na(prtmbnl) ~  prtmbnl,
  !is.na(prtmbanl) ~  prtmbanl,
  !is.na(prtmbbnl) ~  prtmbbnl,
  !is.na(prtmbcnl) ~  prtmbcnl,
  !is.na(prtmbno) ~  prtmbno,
  !is.na(prtmbano) ~  prtmbano,
  !is.na(prtmbpl) ~  prtmbpl,
  !is.na(prtmbapl) ~  prtmbapl,
  !is.na(prtmbbpl) ~  prtmbbpl,
  !is.na(prtmbcpl) ~  prtmbcpl,
  !is.na(prtmbdpl) ~  prtmbdpl,
  !is.na(prtmbpt) ~  prtmbpt,
  !is.na(prtmbapt) ~  prtmbapt,
  !is.na(prtmbbpt) ~  prtmbbpt,
  !is.na(prtmbru) ~  prtmbru,
  !is.na(prtmbaru) ~  prtmbaru,
  !is.na(prtmbbru) ~  prtmbbru,
  !is.na(prtmbse) ~  prtmbse,
  !is.na(prtmbase) ~  prtmbase,
  !is.na(prtmbsi) ~  prtmbsi,
  !is.na(prtmbasi) ~  prtmbasi,
  !is.na(prtmbbsi) ~  prtmbbsi,
  !is.na(prtmbcsi) ~  prtmbcsi,
  !is.na(prtmbsk) ~  prtmbsk,
  !is.na(prtmbask) ~  prtmbask,
  !is.na(prtmbbsk) ~  prtmbbsk,
  !is.na(prtmbtr) ~  prtmbtr,
  !is.na(prtmbatr) ~  prtmbatr,
  !is.na(prtmbua) ~  prtmbua,
  !is.na(prtmbaua) ~  prtmbaua,
  !is.na(prtmbbua) ~  prtmbbua,
  !is.na(prtmbcua) ~  prtmbcua
  ))  %>% 
  select(prtmb) %>% 
  cbind(ess)

table(ess$prtmb)

table(parties3$prtmbit)

# ess %>% 
#   group_by(cntryname, prtmb) %>% 
#   tally()
# 
# ess %>% 
#   select(cntryname, prtvt, prtcl, prtmb) %>% 
#     group_by(cntryname, prtvt, prtcl, prtmb) %>% 
#   tally()

```


# Party Vote for

Important: folgende Länder sind nicht im ESS enthalten:
Latvia

!!!!Folgende Länder sind umkodiert:
UK, Österreich, Ungarn, Spanien, Italien, Griechenland, Dänemark, Belgien, Niederlande, Bulgarien, Schweden, Estonia, Czech Republic, Ireland

## Data preparation

```{r}

#load("data/ess_vote.Rdata")

not_in_ches <- c("Switzerland", "Iceland", "Norway", "Slovenia", "Ukraine", "Russia")

# Check all unique names to exclude "Other" categories
ess %>% 
  select(prtvt) %>% 
  unique()

# Exluding Other Categories
others_na <- c("Other", "Andet - other", "Votó en blanco", "Otros", "Votó nulo", "Andere Partei",
               "Null", "Invalid", "No one", "Altro", "Does not know if voted for a candidate list", 
               "Does not know if voted for a candidate in the 2nd round", 
               "Does not know if voted for a candidate in the 1st round", 
               "Did not vote for a candidate in the 1st round", 
               "No 2nd round in SMD", "Did not vote for a candidate in the 2nd round", "Blank vote",
               "Outro", "Votou em branco / nulo", "Nul", "Blanc", "Autre", 
               "Did not vote for a candidate list", "Autres mouvements écologistes", "Other (nir)", "Spoiled vote")

ess %<>% 
  mutate(prtvt = case_when(
    prtvt %in% others_na ~ NA_character_,
    TRUE ~ prtvt
  )) %>% 
  mutate(prtvt = enc2native(prtvt)) %>%
  mutate(prtvt = str_replace(prtvt, "–", "-")) %>%
  filter(!(cntryname %in% not_in_ches))



#Check how many are Parties are NA
ess %>% 
  select(prtvt) %>% is.na() %>% table()

load("data/populist_parties.Rdata")


populist_parties %>% 
  select(party_cntry, party_name, party_name_english, cluster)

ess %>% 
  filter(cntryname == "Sweden") %>% 
  select(prtvt) %>% 
  table()
#unique(ess$cntryname)
```

## Party Vote Matching

```{r}

#load("data/ess_vote.Rdata")
#table(ess$prtvt)

ess %<>% 
  mutate(populism = case_when(
    
    #Austria
    prtvt == "BZÖ" ~ "Traditionalist Populism",
    prtvt == "FPÖ" ~ "Traditionalist Populism",    
    prtvt == "Team Frank Stronach" ~ "Traditionalist Populism", 
    
    #Bulgaria
    prtvt == "PP Ataka" ~ "Traditionalist Populism",
    str_detect(prtvt, "VMRO") ~ "Traditionalist Populism",   
    # prtvt == "PP VMRO - Balgarsko natsionalno dvizhenie" ~ "Traditionalist Populism", 
    prtvt == "Partia Ataka" ~ "Traditionalist Populism",     
    prtvt == "PP Natsionalen front za dpasenie na Bulgaria" ~ "Traditionalist Populism", 
    #bul_BBT	Bulgaria bez Tsenzura wasn't there in 2014

    #Belgium
    prtvt == "Parti Populaire" ~ "Traditionalist Populism",
    prtvt == "PVDA+" ~ "Progressive Populism",
    prtvt == "Vlaams Belang" ~ "Traditionalist Populism",
    
    #Croatia; 
    prtvt == "Hrvatska stranka prava (HSP)" ~ "Traditionalist Populism",

    #Cyprus; 
    prtvt == "Progressive Party of Working People (AKEL)" ~ "Progressive Populism",
    prtvt == "The Cyprus Green Party" ~ "Progressive Populism",

    #Czech Republic
    prtvt == "KSČM" ~ "Progressive Populism",
    prtvt == "ANO 2011" ~ "Progressive Populism",
    prtvt == "Úsvit přímé demokracie Tomia Okamury" ~ "Traditionalist Populism", 
    #cz_SVOBODNI.... miss you    
    
    #Denmark
    prtvt == "Enhedslisten, De Rød-Grønne - The Red-Green Alliance" ~ "Progressive Populism",
    prtvt == "Enhedslisten - Unity List - The Red-Green Alliance" ~ "Progressive Populism",
    str_detect(prtvt, "Enhedlisten") ~ "Progressive Populism",
    prtvt == "Dansk Folkeparti - Danish peoples party" ~ "Traditionalist Populism",
    #Folkebevægelsen mod EU is missing   
 
    #Spain
    prtvt == "AMAIUR" ~ "Progressive Populism",
    prtvt == "Izquierda Unida (IU)" ~ "Progressive Populism",
    prtvt == "Izquierda Unida (IU) - (ICV en Cataluña)" ~ "Progressive Populism",
    #PODEMOS was created in 2014
    
    #Finland  
    prtvt == "True Finns" ~ "Traditionalist Populism",
    prtvt == "Left Alliance" ~ "Progressive Populism",
    prtvt == "The Left Alliance" ~ "Progressive Populism", 
    
    #Frankreich
    prtvt == "FN (Front National)" ~ "Traditionalist Populism",
    prtvt == "MPF (Mouvement pour la France)" ~ "Traditionalist Populism",
    prtvt == "FDG (Front de Gauche)" ~ "Progressive Populism",
    #prtvt == "Parti Radical de Gauche" ~ "Progressive Populism",    
    #fr_PCF	Parti Communiste Français	
    #fr_PG	Parti de Gauche	
    #fr_Ensemble	Ensemble  --> unter FDG
    #PG, MPF, PCF und Ensamble fehlt
       
    #Deutschland
    prtvt == "NPD" ~ "Traditionalist Populism",
    prtvt == "AfD" ~ "Traditionalist Populism",
    str_detect(prtvt, "Die Linke") ~ "Progressive Populism",
    prtvt == "Piratenpartei" ~ "Progressive Populism",
    #Die Tierpartei not included
    
    #Greece
    prtvt == "Golden Dawn (Xrusi Augi)" ~ "Traditionalist Populism",
    prtvt == "The Coalition of the Radical Left (SYRIZA)" ~ "Progressive Populism",
    prtvt == "The Communist Party of Greece (KKE)" ~ "Progressive Populism",
    prtvt == "The Popular Orthodox Rally (LAOS)" ~ "Traditionalist Populism",
    #prtvt == "Independent Citizens' Movement (SPITHA)" ~ "Traditionalist Populism",
    #ANEL gab es 2010 noch gar nicht :(

    #Hungary
    #prtvt == "Fidesz - KDNP (Fidesz – Magyar Polgári Szövetség Keresztényd" ~ "Traditionalist Populism",
    str_detect(prtvt, "Fidesz") ~ "Traditionalist Populism",
    str_detect(prtvt, "Jobbik") ~ "Traditionalist Populism",
    #prtvt == "Jobbik (Jobbik Magyarországért Mozgalom)" ~ "Traditionalist Populism",
    str_detect(prtvt, "LMP") ~ "Progressive Populism",

    #Ireland
    prtvt == "Green Party" & cntryname == "Ireland" ~ "Progressive Populism",
    prtvt == "Sinn Féin" ~ "Progressive Populism",
    prtvt == "Anti-Austerity Alliance - People Before Profit" ~ "Progressive Populism",
    prtvt == "People Before Profit" ~ "Progressive Populism",
    str_detect(prtvt, "United Left Alliance") ~ "Progressive Populism",
    #prtvt == "Socialist Party - United Left Alliance" ~ "Progressive Populism",

    #Italy
    prtvt == "Movimento 5 Stelle" ~ "Progressive Populism",
    prtvt == "Fratelli d'Italia" ~ "Traditionalist Populism",
    prtvt == "Lega Nord" ~ "Traditionalist Populism",
    prtvt == "Sinistra Ecologia e Libertà (SEL)" ~ "Progressive Populism",
    #it_RC	Partito della Rifondazione Comunista	missing

    #Lithuania
    prtvt == "Electoral Action of Poles in Lithuania (LLRA)" ~ "Traditionalist Populism",
    prtvt == "Party Order and Justice (TT)" ~ "Traditionalist Populism",
    prtvt == "Political Party 'The Way of Courage' (DK)" ~ "Traditionalist Populism",    
    
    #Netherland
    prtvt == "Socialist Party" ~ "Progressive Populism",
    prtvt == "Party for Freedom" ~ "Traditionalist Populism", 
    prtvt == "Party for the Animals" ~ "Progressive Populism",
    #prtvt == "50PLUS" ~ "Progressive Populism",
    
    #Poland
    prtvt == "Law and Justice" ~ "Traditionalist Populism",
    prtvt == "Together Party" ~ "Traditionalist Populism",
    prtvt == "Kukiz'15" ~ "Traditionalist Populism",
    #pol_KNP	Kongres Nowej Prawicy könnte auch Kukiz'15 sein

    #Portugal
    prtvt == "Bloco de Esquerda (BE)" ~ "Progressive Populism",
    prtvt == "Coligação Democrática Unitária (CDU)" ~ "Progressive Populism",
    #por_MPT	Partido da Terra missing

    #Slovakia; 
    prtvt == "Freedom and Solidarity (SaS)" ~ "Progressive Populism",
    prtvt == "Ordinary People and Independent Personalities (OLaNO)" ~ "Traditionalist Populism",
    prtvt == "Slovak National Party (SNS)" ~ "Traditionalist Populism",    
    #slo_SNS	Slovenská národná strana	 Missing    
    
    #Sweden
    prtvt == "FI (Feministiskt initiativ)" ~ "Progressive Populism",
    prtvt == "Piratpartiet" ~ "Progressive Populism", 
#    prtvt == "Sverigedomkraterna" ~ "Traditionalist Populism", 
    stringr::str_detect(ess$prtvt, pattern = "Sverig") ~ "Traditionalist Populism",
    prtvt == "Vänsterpartiet" ~ "Progressive Populism",
      
    #UK
    prtvt == "Green Party" ~ "Progressive Populism",
    prtvt == "UK Independence Party" ~ "Traditionalist Populism",

    # #Estonia
    # prtvt == "Erakond Eestimaa Rohelised" ~ "Progressive Populism",
    # prtvt == "Eesti Vabaerakond" ~ "Progressive Populism",

    is.na(prtvt) ~ NA_character_,
    TRUE ~ "Establishment"
   ))

#save(ess, file = "data/ess.Rdata")

# table(is.na(ess$prtvt))
# table(is.na(ess$prtcl))

# Check if all Partynames have been matched
ess %>% 
  group_by(cntryname, populism, prtvt) %>% 
  tally() %>% 
  select(cntryname, populism) %>% 
  table()

```

## Checking Details

```{r}
table(ess$populism)
table(sjmisc::to_label(ess$cntry))
table(ess$prtvede2)



ess %>% 
  filter(cntryname == "Sweden") %>% 
  select(prtvt) %>% table()

ess %>% 
  filter(cntryname == "Sweden") %>% 
  select(populism) %>% table()

ess %>% 
#  mutate(prtvt = stringi::stri_enc_tonative(prtvt)) %>% 
  mutate(prtvt = enc2native(prtvt)) %>% 
  mutate(prtvt = str_replace(prtvt, "–", "-")) %>% 
  filter(prtvt == "PP VMRO - Balgarsko natsionalno dvizhenie")



ess %>% 
  filter(cntryname == "Bulgaria") %>% 
#  mutate(prtvt = stringi::stri_enc_toascii(prtvt)) %>% 
  mutate(prtvt = enc2native(prtvt)) %>% 
  mutate(prtvt = str_replace(prtvt, "–", "-")) %>%
  select(prtvt) %>% table() %>% dput

ess %>% 
  mutate(prtvt = enc2native(prtvt)) %>%
  mutate(prtvt = str_replace(prtvt, "–", "-")) %>%
  select(prtvt) %>% 
  table()

p_parties <- c("Parti Populaire", "PVDA+", "Vlaams Belang", "Dansk Folkeparti - Danish peoples party", 
               "Enhedslisten - Unity List - The Red-Green Alliance", "NPD", "AfD", "Die Linke", "Piratenpartei",
               "Golden Dawn (Xrusi Augi)", "The Coalition of the Radical Left (SYRIZA)", 
               "The Communist Party of Greece (KKE)", "The Popular Orthodox Rally (LAOS)", "AMAIUR", 
               "Bloque Nacionalista Galego (BNG)", "Izquierda Unida (IU) - (ICV en Cataluña)", "FN (Front National)",
               "MPF (Mouvement pour la France)", "FDG (Front de Gauche)", "Green Party", "Sinn Féin", 
               "Anti-Austerity Alliance - People Before Profit", "Socialist Party - United Left Alliance", 
               "Movimento 5 Stelle", "Fratelli d'Italia", "Lega Nord", "Sinistra Ecologia e Libertà (SEL)",
               "Socialist Party", "Party for Freedom", "Party for the Animals", "50PLUS", "Green Party", 
               "UK Independence Party", "Bloco de Esquerda (BE)", "Coligação Democrática Unitária (CDU)", 
               "BZÖ", "FPÖ", "Team Frank Stronach", "True Finns", "Left Alliance", 
               "FI (Feministiskt initiativ)", "Piratpartiet", "Sverigedomkraterna", "Vänsterpartiet", "PP Ataka", 
               "PP VMRO - Balgarsko natsionalno dvizhenie", "PP Natsionalen front za dpasenie na Bulgaria", 
               "KSČM", "ANO 2011", "Úsvit přímé demokracie Tomia Okamury", "Erakond Eestimaa Rohelised", 
               "Eesti Vabaerakond", "Fidesz - KDNP (Fidesz - Magyar Polgári Szövetség Keresztényd", 
               "Jobbik (Jobbik Magyarországért Mozgalom)", "LMP (Lehet Más A Politika)", 
               "Electoral Action of Poles in Lithuania (LLRA)", "Party Order and Justice (TT)", 
               "Political Party 'The Way of Courage' (DK)", "Law and Justice", "Together Party", 
               "Freedom and Solidarity (SaS)", "Ordinary People and Independent Personalities (OLaNO)", 
               "Hrvatska stranka prava (HSP)", "Progressive Party of Working People (AKEL)",
               "The Cyprus Green Party") #%>% 
#  str_replace("'", "\\'") %>% 
#  paste(collapse = "|") 


#table(str_detect(unique(ess$prtvt), fixed(p_parties)))

compare <- ess %>% 
#  mutate(prtvt = stringi::stri_enc_tonative(prtvt)) %>% 
  mutate(prtvt = enc2native(prtvt)) %>% 
  mutate(prtvt = str_replace(prtvt, "–", "-")) %>% 
  filter(prtvt %in% p_parties) %>% 
  select(prtvt) %>% 
  unique() %>% 
  rbind(data.frame(prtvt = c(NA, NA))) %>% 
  arrange(prtvt) %>% 
  cbind(data.frame(p_parties = sort(p_parties))) %>% 
  mutate(p_parties = as.character(p_parties)) %>% 
  filter(!(p_parties %in% prtvt))
  
ess %>% 
  mutate(sv = stringr::str_detect(ess$prtvt, pattern = "Sverig")) %>% 
  select(sv) %>% table()



ess %>% 
  filter(prtvt == "Sverigedomkraterna")
```


# Party feel closer too


## Data preparation

```{r}
#load("data/ess.Rdata")

not_in_ches <- c("Switzerland", "Iceland", "Norway", "Slovenia", "Ukraine", "Russia")

# Check all unique names to exclude "Other" categories
ess %>% 
  select(prtcl) %>% 
  unique()

# Exluding Other Categories
others_na <- c("Other", "Andet - other", "Votó en blanco", "Otros", "Votó nulo", "Andere Partei",
               "Null", "Invalid", "No one", "Altro", "Does not know if voted for a candidate list", 
               "Does not know if voted for a candidate in the 2nd round", 
               "Does not know if voted for a candidate in the 1st round", 
               "Did not vote for a candidate in the 1st round", 
               "No 2nd round in SMD", "Did not vote for a candidate in the 2nd round",
               "Outro", "Votou em branco / nulo", "Nul", "Blanc", "Autre", 
               "Did not vote for a candidate list", "Autres mouvements écologistes", "Other (nir)", "Autre (precisez)")

ess %<>% 
  mutate(prtcl = case_when(
    prtcl %in% others_na ~ NA_character_,
    TRUE ~ prtcl
  )) %>% 
  mutate(prtcl = enc2native(prtcl)) %>%
  mutate(prtcl = str_replace(prtcl, "–", "-")) %>%
  filter(!(cntryname %in% not_in_ches))



#Check how many are Parties are NA
ess %>% 
  select(prtvt) %>% is.na() %>% table()


populist_parties %>% 
  select(party_cntry, party_name, party_name_english, cluster)

ess %>% 
  filter(cntryname == "United Kingdom") %>% 
  select(prtcl) %>% 
  table()

```

## Party Close Matching

```{r}
#load("data/ess.Rdata")

ess %<>% 
  mutate(popul2 = case_when(

    #Österreich
    prtcl == "BZÖ" ~ "Traditionalist Populism",
    prtcl == "FPÖ" ~ "Traditionalist Populism",    
    prtcl == "Team Frank Stronach" ~ "Traditionalist Populism",  
    
    #Belgium
    prtcl == "Parti Populaire" ~ "Traditionalist Populism",
    prtcl == "PVDA+" ~ "Progressive Populism",
    prtcl == "Vlaams Belang" ~ "Traditionalist Populism",
    
    #Bulgaria
    str_detect(prtcl, "Ataka") ~ "Traditionalist Populism",
    str_detect(prtcl, "VMRO") ~ "Traditionalist Populism", 
    #prtcl == "PP Natsionalen front za dpasenie na Bulgaria" ~ "Traditionalist Populism", 
    #bul_BBT    Bulgaria bez Tsenzura wasn't there in 2014
    #PP Natsionalen front za dpasenie na Bulgaria -> not included
 
    #Croatia; 
    prtcl == "Hrvatska stranka prava (HSP)" ~ "Traditionalist Populism",    
    
    #Czech Republic
    prtcl == "KSCM" ~ "Progressive Populism",
    prtcl == "ANO 2011" ~ "Progressive Populism",
    prtcl == "Úsvit prímé demokracie Tomia Okamury" ~ "Traditionalist Populism", 
    #cz_SVOBODNI.... miss you
    #String bei Úsvit prímé demokracie Tomia Okamury geändert, da anders geschrieben wurde...
    #String KSCM verändert, da ebenso anders geschrieben

    #Denmark
    prtcl == "Dansk Folkeparti - Danish peoples party" ~ "Traditionalist Populism",
    str_detect(prtcl, "Enhedslisten") ~ "Progressive Populism",
    #prtcl == "Enhedslisten - Unity List - The Red-Green Alliance" ~ "Progressive Populism",
    #Folkebevægelsen mod EU is missing   
    
    #Deutschland
    prtcl == "NPD" ~ "Traditionalist Populism",
    prtcl == "AfD" ~ "Traditionalist Populism",
    str_detect(prtcl, "Linke") ~ "Progressive Populism",
    prtcl == "Piratenpartei" ~ "Progressive Populism",
    #Die Tierpartei not included
    
    #Frankreich
    prtcl == "FN (Front National)" ~ "Traditionalist Populism",
    prtcl == "MPF (Mouvement pour la France)" ~ "Traditionalist Populism",
    #prtcl == "FDG (Front de Gauche)" ~ "Progressive Populism",
    prtcl == "PCF (Parti Communiste Francais)" ~ "Progressive Populism",
    prtcl == "PG (Parti de Gauche)" ~ "Progressive Populism",
    #fr_PCF    Parti Communiste Français    
    #fr_PG    Parti de Gauche    
    #fr_Ensemble    Ensemble  --> unter FDG
    #PG, MPF, PCF und Ensamble fehlt
    #Front de Gauche ist eine Wahlplattform, daher wurden die teilnehmenden Parteien hinzugefügt (PG und PCF) und FDG auskommentiert
    
    #Spain
    str_detect(prtcl, "AMAIUR") ~ "Progressive Populism",
    str_detect(prtcl, "Izquierda Unida") ~ "Progressive Populism",
    prtcl == "Podemos" ~ "Progressive Populism",
    #PODEMOS was created in 2014
    
    #Finland  
    prtcl == "True Finns" ~ "Traditionalist Populism",
    str_detect(prtcl, "Left Alliance") ~ "Progressive Populism",
    #prtcl == "The Left Alliance " ~ "Progressive Populism",

    #Greece
    prtcl == "Golden Dawn (Xrusi Augi)" ~ "Traditionalist Populism",
    prtcl == "The Coalition of the Radical Left (SYRIZA)" ~ "Progressive Populism",
    prtcl == "The Communist Party of Greece (KKE)" ~ "Progressive Populism",
    prtcl == "The Popular Orthodox Rally (LAOS)" ~ "Traditionalist Populism",
    #prtcl == "Independent Citizens' Movement (SPITHA)" ~ "Traditionalist Populism",
    #ANEL gab es 2010 noch gar nicht :(

    #Hungary
    str_detect(prtcl, "Jobbik") ~ "Traditionalist Populism",
    str_detect(prtcl, "LMP") ~ "Progressive Populism",
    #prtcl == "Fidesz (Fidesz Magyar Polgári Párt)" ~ "Traditionalist Populism",
    str_detect(prtcl, "Fidesz") ~ "Traditionalist Populism",
    #Fidez geändert, da keine Koalition...

    #Ireland
    prtcl == "Green Party" ~ "Progressive Populism",
    prtcl == "Sinn Féin" ~ "Progressive Populism",
    prtcl == "Anti-Austerity Alliance - People Before Profit" ~ "Progressive Populism",
    prtcl == "People Before Profit" ~ "Progressive Populism",
    str_detect(prtcl, "United Left Alliance") ~ "Progressive Populism",

    #Italy
    prtcl == "Movimento 5 Stelle" ~ "Progressive Populism",
    prtcl == "Fratelli d'Italia" ~ "Traditionalist Populism",
    prtcl == "Lega Nord" ~ "Traditionalist Populism",
    prtcl == "Sinistra Ecologia e Libertà (SEL)" ~ "Progressive Populism",
    #it_RC    Partito della Rifondazione Comunista    missing

    #Lithuania
    prtcl == "Electoral Action of Poles in Lithuania (LLRA)" ~ "Traditionalist Populism",
    prtcl == "Party Order and Justice (TT)" ~ "Traditionalist Populism",
    prtcl == "Political Party 'The Way of Courage' (DK)" ~ "Traditionalist Populism",

    #Netherlands
    prtcl == "Socialist Party" ~ "Progressive Populism",
    prtcl == "Party for Freedom" ~ "Traditionalist Populism", 
    prtcl == "Party for the Animals" ~ "Progressive Populism",
    prtcl == "PVV (List Wilders)" ~ "Traditionalist Populism",
    
    #Poland
    prtcl == "Law and Justice" ~ "Traditionalist Populism",
    prtcl == "Together Party" ~ "Traditionalist Populism",
    prtcl == "Kukiz'15" ~ "Traditionalist Populism",
    prtcl == "United Poland" ~ "Traditionalist Populism",
    #pol_KNP    Kongres Nowej Prawicy könnte auch Kukiz'15 sein
    #Kukiz drin, dahe rhinzugefügt
    
    #UK
    prtcl == "Green Party" ~ "Progressive Populism",
    prtcl == "UK Independence Party" ~ "Traditionalist Populism",

    #Portugal
    prtcl == "Bloco de Esquerda (BE)" ~ "Progressive Populism",
    prtcl == "CDU - Coligação Democrática Unitária (PCP-PEV)" ~ "Progressive Populism",
    #por_MPT    Partido da Terra missing

    #Sweden
    prtcl == "FI (Feministiskt initiativ)" ~ "Progressive Populism",
    prtcl == "Piratpartiet" ~ "Progressive Populism", 
    str_detect(prtcl, "Sverige") ~ "Traditionalist Populism", 
    prtcl == "Vänsterpartiet" ~ "Progressive Populism",

# 
#     #Estonia
#     prtcl == "Erakond Eestimaa Rohelised" ~ "Progressive Populism",
#     prtcl == "Eesti Vabaerakond" ~ "Progressive Populism",

    #Slovakia; 
    prtcl == "Freedom and Solidarity (SaS)" ~ "Progressive Populism",
    prtcl == "Ordinary People and Independent Personalities (OLaNO)" ~ "Traditionalist Populism",
    prtcl == "Slovak National Party (SNS)" ~ "Traditionalist Populism",    

    #slo_SNS    Slovenská národná strana     Missing

    #Cyprus; 
    prtcl == "Progressive Party of Working People (AKEL)" ~ "Progressive Populism",
    prtcl == "The Cyprus Green Party" ~ "Progressive Populism",
    
    is.na(prtcl) ~ NA_character_,
    TRUE ~ "Establishment"
   ))

  ess %>% 
    group_by(cntryname, popul2, prtcl) %>% 
    tally() %>% 
    select(cntryname, popul2) %>% 
    table()



save(ess, file = "data/ess.Rdata")
```

## Checking Details

```{r}

# Check if Party Names are the different
ess %>% 
  filter(cntryname == "Spain") %>% 
  select(prtvt) %>% table()

# Check if Party Names are found
ess %>% 
  filter(prtvt == "Jobbik (Jobbik Magyarországért Mozgalom)")

table(ess$popul2)

ess %>% 
#  filter(cntryname == "Bulgaria") %>% 
#  mutate(prtvt = stringi::stri_enc_toascii(prtvt)) %>% 
  mutate(prtcl = enc2native(prtcl)) %>% 
  mutate(prtcl = str_replace(prtcl, "–", "-")) %>%
  mutate(prtcl = as.character(prtcl)) %>% 
  select(prtcl)  %>% unique %>%  dput()


```

# Merging Time

```{r}
# table(ess$prtvt == ess$prtcl)
  

ess %<>% 
  mutate(target = case_when(
    is.na(populism) ~ popul2,
    is.na(popul2) ~ populism,
    populism != popul2 & !is.na(popul2) ~ popul2,
    TRUE ~ populism
  )) #%>% 
  #select(target) %>% 
  #table()

ess %>% 
  select(populism) %>% 
  table()

ess %>%
  select(populism, popul2, target)

save(ess, file = "data/ess.Rdata")
```





# Plotting Stuff

## Plotting Populist Distributions

```{r}
load("data/ess.Rdata")

library(questionr)

calc_perc <- function(variable = ess$populism, weight = ess$pweight) {
  
  perc_table <- questionr::wtd.table(variable, weights = weight) 
  Illib_Popul <- c((perc_table[2] / (perc_table[1] + perc_table[2] + perc_table[3])) * 100, perc_table[2])
  Liberal_Popul <- c((perc_table[3] / (perc_table[1] + perc_table[2] + perc_table[3])) * 100, perc_table[3])
  Establishment <- c((perc_table[1] / (perc_table[1] + perc_table[2] + perc_table[3])) * 100, perc_table[1])

  return(tibble::tibble(Illib_Popul, Liberal_Popul, Establishment))
}

calc_perc()
calc_perc(variable = ess$target)


ess %>% 
  select(populism, cntryname) %>% 
  mutate(populism = as.factor(populism)) %>% 
  ggplot(aes(populism, fill = cntryname)) +
  geom_bar() +
  facet_wrap(~cntryname, ncol = 2, scales = "free_y")

ggsave(filename = "images/distrib_cntry.png", height = 10)

sjPlot::sjp.grpfrq(ess$populism,
           ess$cntryname, 
           title = NULL,
           show.summary = TRUE,
           summary.pos = "l", 
           coord.flip = T,
           weight.by = ess$pweight)

dput(unique(as.character(ess$cntryname)))

countries <- c("Bulgaria", "Cyprus", "Denmark", "Spain", "Greece", "Croatia", 
"Hungary", "Italy", "Lithuania", "Portugal", "Slovakia", "Austria", 
"Belgium", "Czech Republic", "Germany", "Estonia", "Finland", 
"France", "United Kingdom", "Ireland", "Netherlands", "Poland", 
"Sweden")

for (jj in seq_along(countries)) {
  plot_ess <- ess %>% 
    mutate(cntryname = as.character(cntryname)) %>% 
    mutate(populism = as.character(populism)) %>% 
    filter(cntryname == countries[jj])
  
  countryplot <- sjp.frq(plot_ess$populism, 
        title = paste0("Populism Distribution: ", countries[jj]),
        coord.flip = TRUE)
  
  cat(countries[jj], ":", jj, "\n")
  
  ggsave(countryplot$plot, filename = paste0("images/popul_cntry/popul_", countries[jj], ".png"))
}

countryplot <- sjp.frq(ess$populism, 
        title = "Populism Distribution: All Countries",
        coord.flip = TRUE)
 
ggsave(countryplot$plot, filename = "images/popul_cntry/popul_all.png")
```

## Descriptives

```{r}
load("data/ess.Rdata")

#pacman::p_install_gh("systats/binoculaR")
library(rstan)
binoculaR::binoculaR(ess)

var_label(ess$imueclt)

rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ()) # Run on multiple cores

set.seed(3875)

#ir <- data.frame (scale (iris[, -5]), Species=iris[, 5])

mlogit_ess <- ess %>% 
  mutate(target = as.factor(target)) %>% 
  drop_na(target) %>% 
  mutate(cltre_ndrmnd = 10 - imueclt) %>% 
  mutate(stsfd_econ = 10 - stfeco)

mlogit_ess %>% 
  ggplot(aes(target, cltre_ndrmnd, group = target, fill = target)) +
  geom_boxplot() +
  ggthemes::theme_fivethirtyeight() +
  ggthemes::scale_fill_fivethirtyeight()

mlogit_ess %>% 
  ggplot(aes(target, stsfd_econ, group = target, fill = target)) +
  geom_boxplot() +
  ggthemes::theme_fivethirtyeight() +
  ggthemes::scale_fill_fivethirtyeight()
```


# Mlogit

```{r}
load("data/ess.Rdata")

#pacman::p_install_gh("systats/binoculaR")
library(rstan)
binoculaR::binoculaR(ess)

var_label(ess$imueclt)

rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ()) # Run on multiple cores


mlogit_ess <- ess %>% 
  mutate(populism = as.factor(populism)) %>% 
  drop_na(prtvt) %>% 
  mutate(cltre_ndrmnd = 10 - imueclt) %>% 
  mutate(stsfd_econ = 10 - stfeco)

set.seed(3875)

### With improper prior it takes about 12 minutes, with about 40% CPU utilization and fans running,
### so you probably don't want to casually run the next line...

library(nnet)
mlogit_ess$populism2 <- relevel(mlogit_ess$target, ref = "Establishment")
test <- multinom(populism2 ~ cltre_ndrmnd + stsfd_econ, data = mlogit_ess, weights = pweight)

summary(test)

z <- summary(test)$coefficients/summary(test)$standard.errors
z

# 2-tailed z test
p <- (1 - pnorm(abs(z), 0, 1)) * 2
p

## extract the coefficients from the model and exponentiate
exp(coef(test))

head(pp <- fitted(test))

library(mlogit)
m <- mlogit(populism2 ~ cltre_ndrmnd, data = mlogit_ess)
# compute a data.frame containing the mean value of the covariates in the sample
z <- with(mlogit_ess, data.frame(price = tapply(price, index(m)$alt, mean), 
	catch = tapply(catch, index(m)$alt, mean), 
income = mean(income)))
# compute the marginal effects (the second one is an elasticity
effects(m, covariate = "income", data = z)
effects(m, covariate = "price", type = "rr", data = z)
effects(m, covariate = "catch", type = "ar", data = z)

system.time (b1 <- brm (populism ~ cltre_ndrmnd, 
                        data=mlogit_ess,
                        family="categorical", 
                        n.chains=3, 
                        n.iter=3000, 
                        n.warmup=600))

```