---
geometry: "left=2.5cm,right=4cm,top=2.5cm,bottom=2cm"
output: 
  bookdown::pdf_book:
    toc: false
    includes:
     in_header: header.tex
     before_body: title_page.tex
#     after_body: appendix.tex
documentclass: article
bibliography: references.bib
#cls: systats.cls
csl: university-of-stuttgart-sowi-standards.csl
link-citations: yes
---

```{r globalchunks, include=FALSE}
# Default Options - kann bei Gebrauch geändert werden
knitr::opts_chunk$set(
  echo = T # Whether to display code along with its results
  , eval = T # Whether to evaluate the code and include its results
  , results = "asis" # this at deafult is in end much more efficient
  , cache = F # Whether to cache results for future renders (efficient!)
  , warning = F # Whether to display errors
  , message = F # Whether to display messages
  , error = F # maybe turn on
  , tidy = F # Whether to reformat code in a tidy way when displaying it
  , fig.width = 6 # plot width at 6
  , fig.height = 4 # plot height at 4
  , fig.align = "left" # plot alignment center
)

options(xtable.comment = FALSE, scipen = 9999)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

x <- 1233.34
y <- 44864
z <- 34.876
```


<!-- \onehalfspacing -->
\setstretch{1.5}

# Introduction


```{r child = '1_intro.Rmd'}
```

This is a great way to test whether $`r x`$ really works in the way it is intended to work. This is different though becasue $`r toString(z)`$ might be better actually. Or how about $`r I(y)`$.

`r x`

`r toString(x)`

`r I(x)`

The following subsection will conceptualize regime support and introduce possible explanatory frameworks that were gathered from the relevant literature (Section 2.1). In this section, the concept of deliberation is clarified (Section 2.2) and a link between deliberation and regime support is established, from which research hypotheses are subsequently derived (Section 2.3). 


# Theory

**Some Citations**

This is an example introduction. Let's cite someone here [@easton1965systems]. And in text as well: @habermas1994three says that we can cite people in text. Or we can write the name, and than use the citation thingy to print the year: Blabla states something about something [-@easton1975re]. Or how about multiple citations [@habermas1994three; @habermas1994three]. Or we citation with a little of text around it [for example see @habermas1994three: 92-93].

ALLE Zitierweisen von Zotero gibts [HIER](https://www.zotero.org/styles).


**More Citations**

Blah blah [cf. @easton1965systems, pp. 33-35; also @easton1975re, pp. 2].

Blah blah [@easton1975re, pp. 33-35, 38-39].

Blah blah [@easton1975re; @habermas1994three].

Smith says blah [-@easton1975re].

@easton1975re says blah.

@habermas1994three [p. 33] says blah.



```{r child = '2_theory.Rmd'}
```

# Methodological and Analytical Section

```{r child = '3_methods.Rmd'}
```

# Analysis

```{r child = '4_analysis.Rmd'}
```

# Conclusions

```{r child = '5_conclusions.Rmd'}
```


\setstretch{1}

\newpage

# References
